Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-06-26 doc/JFLA2022/Slides/Slides.tex
last changes in Slides ?

\begin{block}{Definition:}
  \textcolor{mathcolor}{$H'_\alpha(i)$} is the least $l$ such that \textcolor{mathcolor}{$\alpha_l=0$} (cf. previous slide).

@@

$H'$ is a slight variant of the \emph{Hardy Hierarchy}. In \coq, we implement it with the \texttt{equations} plug-in.
\end{block}

\begin{block}{Example:}
  {\color{mathcolor}
  $$      H'_{\omega^\omega}(i)=\, \textbf{let}\,F\;f\;k := f^{(k+1)}(k)\,
                                  \textbf{in}\, F^{(i)}(\lambda k.\,2k+1)\,i$$
}
\end{block}

>>>>

\textbf{Definition: }
  \textcolor{mathcolor}{$H'_\alpha(i)$} is the least $l$ such that \textcolor{mathcolor}{$\alpha_l=0$} (cf. previous slide).

@@

\textcolor{mathcolor}{$H'$} is a slight variant of the \emph{Hardy Hierarchy} (defined by transfinite recursion with \texttt{equations}).
 We can prove exact, but not always very readable, formulas for small values of \textcolor{mathcolor}{$\alpha$} (\emph{e.g.} \textcolor{mathcolor}{$\omega^\omega$}).

\inputsnippets{./HprimePhi0OmegaClosed}
